Hydras \& Co.

### 2022-12-05 doc/hydras.tex
minor changes
Minor changes in Latex files
New notations (#139)
* experiment fol notations

* first attempts

* experiment FOL notations

* experiment FOL notations

* minor change

* minor change

* minor change

* experimental notations

* experimental notations

* minor changes, bullets in folLogic

* bulletizing folLogic.v (half done, to resume at forallE)

* bulletized folLogic.v

* Example of folLogic

* more examples

* drinkers theorem in FOL (clumsy draft)

* re-structuring prro scripts in folLogic2

* re-structuring proof scripts in folLogic[23]

\title{Hydras \& Co.}
%\pagestyle{fancy}
%\fancyhead{Hydras, Ordinals, \& Co.}
\makeindex{gaiabridge}
\makeindex{coq}
\makeindex{maths}
\makeindex{hydras}
\makeindex{additions}
\makeindex{primrec}
\begin{document}
\begin{titlepage}
   \begin{center}
       \vspace*{1cm}

@@

       \emph{Pierre Castéran, LaBRI, Univ. Bordeaux, CNRS UMR 5800\\ \textbf{email:} pierre dot casteran arobas gmail dot com. \\ With contributions by Yves Bertot, Ilm\={a}rs C\={i}rulis, \'Evelyne Contejean,  Jérémy Damour, Florian Hatat, Pascal Manoury, Karl Palmskog, Clément Pit-Claudel, and Théo Zimmermann. \\ The formalization of primitive recursive functions was originally authored by Russel O'Connor.}%\cite{OConnor05}.}

@@

\printindex{gaiabridge}{Links to \gaia Library}
\label{gaia-index}
\printindex{coq}{Coq, plug-ins and standard library}
\printindex{maths}{Mathematical notions and algorithmics}
%\printindex{hydras}{Library hydras: Ordinals and hydra battles}
%\printindex{primrec}{Library hydras.Ackermann: Primitive recursive functions}
%\printindex{additions}{Library additions: Addition chains}

>>>>

\title{Hydras \& Co.}
%\pagestyle{fancy}
%\fancyhead{Hydras, Ordinals, \& Co.}
\makeindex{gaiabridge}
\makeindex{coq}
\makeindex{maths}
\makeindex{hydras}
\makeindex{additions}
\makeindex{ackermann}
\begin{document}
\begin{titlepage}
   \begin{center}
       \vspace*{1cm}

@@

       \emph{Pierre Castéran, LaBRI, Univ. Bordeaux, CNRS UMR 5800\\ \textbf{email:} pierre dot casteran arobas gmail dot com. \\ With contributions by Yves Bertot, Ilm\={a}rs C\={i}rulis, \'Evelyne Contejean,  Jérémy Damour, Florian Hatat, Pascal Manoury, Karl Palmskog, Clément Pit-Claudel, and Théo Zimmermann. \\ The formalization of primitive recursive functions and Peano Arithmetic was originally authored by Russel O'Connor.}%\cite{OConnor05}.}

@@

\printindex{gaiabridge}{Links to \gaia Library}
\label{gaia-index}
\printindex{coq}{Coq, plug-ins and standard library}
\printindex{maths}{Mathematical notions and algorithmics}
\printindex{hydras}{Library hydras: Ordinals and hydra battles}
\printindex{ackermann}{Library hydras.Ackermann: Primitive recursive functions, G\"{o}del encoding}
\printindex{additions}{Library additions: Addition chains}
